\section{Future Work}
Future work could be summarized into three categories. Creature expansions, Board expansions and System Expansions.

\subsection{Creature Expansions}
Creature expansion to the system could take place in several forms. An expanded neural network system for the creatures should be tested. This could help both species of creatures develop more complex behaviour. An additional change that could be made to creatures is tho provide each creature a line of sight that would replace the entire board as an input. This way the simulation is more realistic to real life and both the predator and prey would have to learn to situations without full knowledge of the board. Another set of experiments could be to simplify the predator's movement and remove the chasing in the x and the y direction. This would reduce the complexity of the network and potentially provide a more even evolution between the two creatures.


\subsection{Board Expansions}
Board expansions that should be tested include expanding the board for multiple sizes in order to increase or restrict the freedom to move as the smaller the board size, the more interaction there will be between the creatures. Another expansion should add a border to the board which can be used by the creatures as input to give a warning that the edge of the board is there. That way, the behaviour that is developed in V1 of the came could be more direct as both the predator and the prey would know exactly where the board ends. Some type of terrain could also be added. This could include mountains which could take place as a wall where the creatures cannot move, or traps which would cause the creatures to lose if it was stepped on.


\subsection{System Expansions}
The obvious next steps for this system expansion is to introduce a team dynamic. That is, add multiple predators and prey competing against each other. This could introduce interesting teamwork mechanics such as working together to corner a prey. The neural networks for these predators could come from the same swarm, or more swarms could be introduced. If more swarms are introduced, then sub-specializations could potentially evolve. In case of predators, there could be one that could become the chaser and another one that could be be ambusher. Similarly, for prey there might be one swarm that evolves to be sacrifices for the benefit of the group.