\newpage

\begin{thebibliography}{9}
\bibitem{englebrecht-pso}
F. van den Bergh, A.P. Engelbrecht, ''A study of particle swarm optimization particle trajectories'', \url{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.142.2258&rep=rep1&type=pdf}, [Online, accessed 2-May-2017].
%http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.142.2258&rep=rep1&type=pdf




\bibitem{Langenhoven-2006}
LH. Langenhoven, ''Evolving Behaviour through Competition Special Project'', Master's thesis, University of Pretoria, November 2006.

\bibitem{Scheepers-2013}
C. Scheepers, ''Coevolution of Neuro-controllers to Train Multi-Agent Teams from Zero Knowledge'', Master's thesis, University of Pretoria, July 2013.

\bibitem{apache}
Apache Commons: Commons Math, \url{http://commons.apache.org/proper/commons-math/userguide/linear.html}, [Online, Accessed 4-May-2017].

\bibitem{Sonali}
S.B. Maind, P. Wankar, ''Research Paper on Basic of Artificial Neural Network'', in \textit{International Journal on Recent and Innovation Trends in Computing and Communication}, Vol. 2, Issue. 1, pp. 96-100, 2014.

\bibitem{deep-learning-book}
I. Goodfellow, Y. Bengio, and A. Courville, Deep Learning. MIT Press, 2016. \url{http: //www.deeplearningbook.org}, [Online, Accessed 4-May-2017].

%\bibitem{Rahmani}
%M. Rahmani, ''\textit{Particle swarm optimization of artificial neural networks for autonomous robots}'', Master's thesis, Chalmers University of Technology, 2008

%\bibitem{Unger}
%N. Unger, ''\textit{Cooperative Particle Swarm Optimization in Dynamic Environments}'', Master's thesis, Brock University, 2012

%\bibitem{}
%T.M.Blackwell, P. J. Bentley, ''\textit{Dynamic Search with Charged Swarms}'', \url{https://pdfs.semanticscholar.org/4195/ad7025e93a4ff55b1b3dc11162b5edf32d36.pdf} [Online, Accessed 2-May-2017]



%\bibitem{robocup}
%Robocup website, \url{http://www.robocup.org} [Online, Accessed 02-May-2017]

%\bibitem{fira}
%Federation of International Robot-soccer Association, \url{http://www.fira.net/main/} [Online, Accessed 2-May-2017]

\bibitem{pso-pseudocode-ref}
J. Brownlee, ''Particle Swarm Optimization Pseudocode'', \url{http://www.cleveralgorithms.com/nature-inspired/swarm/pso.html} [Online, Accessed 2-May-2017].

\bibitem{neuron}
G. Orr, ''A Simple Artificial Neuron'', \url{https://www.willamette.edu/~gorr/classes/cs449/ann-overview.html} [Online, Accessed 2-May-2017].

\bibitem{neural-net}
S.H. Chun, ''Coursera Neural Networks for Machine Learning Week1 - Neural Network and Machine Learning'', \url{http://sanghyukchun.github.io/39/} [Online, Accessed 2-May-2017].

\bibitem{kennedy}
J. Kennedy, R. Eberhart, ''Particle Swarm Optimization'', 1995, \url{https://www.cs.tufts.edu/comp/150GA/homeworks/hw3/_reading6\%201995\%20particle\%20swarming.pdf}, [Online, Accessed 4-May-2017].

\bibitem{charged-pso-slides}
A.P. Engelbrecht, ''Particle Swarm Optimization in Dynamic Environments'', \url{http://goanna.cs.rmit.edu.au/~xiaodong/aciss09/tute-slides/dynamicPSO.pdf} [Online, Accessed 2-May-2017].

\bibitem{Rosin}
C. D. Rosin, R. K. Belew, ''New Methods for Competitive Coevolution'', Unknown, \url{http://www.sci.brooklyn.cuny.edu/~sklar/teaching/f05/alife/papers/rosin-96coev.pdf}, [Online, Accessed 4-May-2017].

\bibitem{coevolution-chess}
O. E. David et al., ''Genetic Algorithms for Evolving Computer Chess Programs'', in \textit{IEEE Transactions on Evolutionary Computation}, Vol. 18, Issue. 15, pp. 779 - 789, 2014.

\bibitem{Lubberts}
A. Lubberts, R. Miikkulainen, ''Co-Evolving a Go-Playing Neural Network'', In \textit{Coevolution: Turning Adaptive Algorithms upon Themselves, Birds-of-a-Feather Workshop, Genetic and Evolutionary Computation Conference (Gecco-2001)}, 2011, \url{www.cs.utexas.edu/~ai-lab/pubs/lubberts.coevolution-gecco01.ps.gz}, [Online, Accessed 5-May-2017].

\bibitem{Yong}
C. H. Yong, R. Miikkulainen, ''Cooperative Coevolution of Multi-Agent Systems'', Unknown, \url{http://nn.cs.utexas.edu/downloads/papers/yong.tr287.pdf}, [Online, Accessed 5-May-2017].

\bibitem{Runka}
A. Runka, ''Genetic Programming for the RoboCup Rescue Simulation System'', Master's Thesis, 2010, \url{http://rd.library.brocku.ca/bitstream/handle/10464/3184/Brock_Runka_Andrew_2010.pdf?sequence=1}, [Online Accessed 5-May-2017]


\bibitem{Hawe}
G. I. Hawe et al., ''Agent-based simulation of emergency response to plan the allocation of resources for a hypothetical two-site major incident'' in \textit{Engineering Applications of Artificial Intelligence}, Vol. 46, Part. B, pp. 336–345, 2015, \url{http://www.sciencedirect.com/science/article/pii/S0952197615001451}, [Online, Accessed 5-May-2017]

\bibitem{neat}
K. O. Stanley, R. Miikkulainen, ''Evolving Neural Networks through Augmenting Topologies'', 2002, \url{http://nn.cs.utexas.edu/downloads/papers/stanley.ec02.pdf}, [Online, Accessed 5-May-2017]

\bibitem{koehn}
P. Koehn, ''Combining Genetic Algorithms and Neural Networks: The Encoding Problem'', Master's thesis, The University of Tennessee, 1994, \url{http://homepages.inf.ed.ac.uk/pkoehn/publications/gann94.pdf}, [Online, Accessed 5-May-2017]

\bibitem{yann}
Y. Lecun et all., ''Efficient BackProp'', Unknown, \url{http://yann.lecun.com/exdb/publis/pdf/lecum-98b.pdf}, [Online, Accessed 5-May-2017]

\bibitem{Garro}
B. A. Garro et al., ''Evolving Neural Networks: A Comparison between Differential Evolution and Particle Swarm Optimization'', Unknown, \url{https://link.springer.com/chapter/10.1007/978-3-642-21515-5_53}, [Online, Accessed 5-May-2017]


\end{thebibliography}

